Type theories as quotient inductive-recursive types

### 2025-02-19 tex/main.tex
comment out het eq

\subparagraph*{Heterogeneous identity}
In our implementation, some statements are proved differently from our presentation. 
We have sometimes used John Major equality~\cite{McBride1999} $x \cong y$  for $A, B : \Set$, and $x : A$ and $y : B$, where dependent congruence rule or dependent identity type are needed.

For instance, in \cref{ex:pi-comp-qiirt}, the identity $\pi_2(\sigma ; \tau) = \pi_2(\sigma; (\pi_1 \tau, \pi_2 \tau)$ could be proved by $\apdfunc f \colon (p : x =^A y) \to f\,x =^{P}_{p} f\,y$ and the equality constructor $\pi\eta : \tau = (\pi_1\tau, \pi_2\tau)$, resulting an additional transport to remove later.
However, as $\subTy{A}{\pi_1(\sigma; \tau)}$ and $\subTy{A}{\pi_1(\sigma; (\pi_1\tau, \pi_2\tau))}$ are strictly equal, the resulting identity is indeed homogeneous.
Hence, we use the heterogeneous congruence $\mathit{hap}_f\colon (p : x \simeq y) \to f\,x\simeq f\,y$ (by \lstinline|hcong|) and switch back to the ordinary identity type $f\,x = f\, y$ (by \lstinline|≅-to-≡|) as their types match.

%As shown by McBride, the heterogeneous identity type is equivalent to the ordinary identity type equipped with the principle of uniqueness of identity proofs.

\LT[noinline]{Mention the NbE for SC here?}

>>>>

%\subparagraph*{Heterogeneous identity}
%In our implementation, some statements are proved differently from our presentation. 
%We have sometimes used John Major equality~\cite{McBride1999} $x \cong y$  for $A, B : \Set$, and $x : A$ and $y : B$, where dependent congruence rule or dependent identity type are needed.
%
%For instance, in \cref{ex:pi-comp-qiirt}, the identity $\pi_2(\sigma ; \tau) = \pi_2(\sigma; (\pi_1 \tau, \pi_2 \tau)$ could be proved by $\apdfunc f \colon (p : x =^A y) \to f\,x =^{P}_{p} f\,y$ and the equality constructor $\pi\eta : \tau = (\pi_1\tau, \pi_2\tau)$, resulting an additional transport to remove later.
%However, as $\subTy{A}{\pi_1(\sigma; \tau)}$ and $\subTy{A}{\pi_1(\sigma; (\pi_1\tau, \pi_2\tau))}$ are strictly equal, the resulting identity is indeed homogeneous.
%Hence, we use the heterogeneous congruence $\mathit{hap}_f\colon (p : x \simeq y) \to f\,x\simeq f\,y$ (by \lstinline|hcong|) and switch back to the ordinary identity type $f\,x = f\, y$ (by \lstinline|≅-to-≡|) as their types match.
% 
%%As shown by McBride, the heterogeneous identity type is equivalent to the ordinary identity type equipped with the principle of uniqueness of identity proofs.
%
%\LT[noinline]{Mention the NbE for SC here?}
